Footpath Planning for Example-driven Procedural Road Networks

### 2020-03-27 paper/paper.tex
Add source of error section to report
Add seciton about OSM-SLU-specific data preprocessing

@@

>>>>

\subsection{Specific preprocessing for SLU-OSM geodata}

The SLU map is delivered with cropped buildings to exactly matched the query coordinates. This means that area comparsion will not work.
Therefore it was neccessary to crop both datasets to ensure that all buildings were complete and had matching candidates in the other set.
(Show a picture)

@@

\section{Analysis}

(Fan et al, 2014) claimed that the positional error is largely due to the limited resolution in satellite imagery.
